Paper

### 2024-12-12 paper/index.qmd
manuscript

---
title: Paper
authors:
  - name: Alessandro Gerada
    affiliation: University of Liverpool
    roles: writing
    corresponding: true
bibliography: references.bib
---

@@

-   $x_p(t) = 0$ if patient $p$ is not infected/colonised at time $t$,
-   $x_p(t) = 1$ if patient $p$ is infected/colonised at time $t$. It was assumed that infection/colonisation was not reversible during the simulation, i.e., that infected/colonised patients remained so until discharge. Therefore, in contrast to a traditional susceptible-infected-recovered model [@anderson1991], this model was defined as:

@@

-   $H_S$ is the number of susceptible inpatients,
-   $H_I$ is the number of infected inpatients,
-   $A_S$ is the rate of new susceptible admissions,
-   $A_I$ is the rate of new infected admissions,
-   $Q$ is the rate of transmission,
-   $D$ is the rate of patients that are discharged.

The hospital capacity was constantly kept at 100% occupancy, therefore:

@@

@@

| Name                                                       | Value    | Description                                                             | Reference                |
|------------------|------------------|--------------------|------------------|
| Baseline (pre-outbreak) antimicrobial prescription rate    | 0.319    | Proportion of patients administered antimicrobials during admission     | @versporten2018          |
| Admission duration                                         | 8.3 days | Mean of a Poisson distribution                                          | @thehealthfoundation2023 |
| Proportion of toilets that are shared between \>1 patients | 0.6      | The remaining proportion (0.4) of toilets were dedicated to one patient | N/A                      |

@@

```{r}
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| warning: false
#| label: fig-posterior-densities
#| fig-cap: "Changes in parameters during outbreak and enhanced infection control periods. Density plots show the posterior distributions of key simulation parameters after calibration using approximate Bayesian computation."
#| fig-subcap:
#|   - "General parameters"
#|   - "Toilet-related parameters"
#| layout-ncol: 1
abc_params_outbreak_control$unadj.values %>% 
  as_tibble %>% 
  dplyr::select(-`outbreak-start`, -`outbreak-end`, -`control-end`,
                -`antibiotic-effect`,
                -`random-colonisation`) %>% 
  dplyr::select(!contains("toilet")) %>% 
  pivot_longer(cols=everything()) %>%
  mutate(type = case_when(
    str_starts(name, "o-") ~ "Outbreak",
    str_starts(name, "c-") ~ "Control",
    .default = "Baseline")) %>%
  mutate(name = str_remove(name, "^o-|^c-")) %>%
  mutate(name = str_replace_all(name, "-", " ")) %>%
  mutate(name = str_to_title(name)) %>% 
  # change type to ordered factor
  mutate(type = factor(type, levels = c("Baseline", "Outbreak", "Control"))) %>%
  ggplot(aes(x = value, ..scaled.., fill = type)) +
  geom_density(alpha = 0.1) +
  facet_wrap(~name, scales = "free_x") +
  # remove y axis
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("Parameter value") + 
  theme(legend.title = element_blank(),
        text=element_text(size=24)) + 
  # manually set colors
  scale_fill_manual(values = c("Baseline" = "green", "Outbreak" = "red", "Control" = "blue"))

>>>>

---
title: Paper
authors:
  - name: Alessandro Gerada
    affiliation: University of Liverpool
    roles: writing
    corresponding: true
---

@@

-   $x_p(t) = 0$ if patient $p$ is not infected/colonised at time $t$,
-   $x_p(t) = 1$ if patient $p$ is infected/colonised at time $t$. It was assumed that infection/colonisation was not reversible during the simulation, i.e., that infected/colonised patients remained so until discharge. Hence, in contrast to a traditional susceptible-infected-recovered model [@anderson1991], the differential equations of this model were:

@@

-   \$dH_s/dt\$ is the rate of
-   $H_S$ is the number of susceptible inpatients,
-   $H_I$ is the number of infected inpatients,
-   $A_S$ is the rate of new susceptible admissions,
-   $A_I$ is the rate of new infected admissions,
-   $Q$ is the transmission coefficient,
-   $D$ is the rate of patients that are discharged.

The hospital capacity was constantly kept at 100% occupancy (i.e., patients were immediately replaced on discharge), therefore:

@@

At each time increment, the probability of a non-colonised/infected patient acquiring infection (i.e., transitioning from a non-infected/colonised to infected/colonised state) depended on: 1) a baseline risk of *de novo* infection/colonisation:

$$ 
P_\text{de novo}(t) = 1 - \exp {( - r_0 T(t) )}
$$

and 2) the usage of contaminated toilets:

$$
P_\text{toilet}(t) = 1 - \exp ( {-\sum_{j=0}^{U_i(t)}[C(t_j) \cdot T(t)]} )
$$

Administration of antimicrobial therapy modified the risk of infection/colonisation.

$$
R_i(t) = r_0 \cdot T(t) + \sum_{j=0}^{U_i(t)}[C(t_j) \cdot T(t)]
$$

-   $R_i(t)$ is the risk of patient $i$ acquiring infection/colonisation at time $t$,

-   $r_0$ is the baseline/*de novo* risk of infection/colonisation,

-   $T(t)$ is a binary indicator for antimicrobial therapy:

$$
\mathrm{T}(t) = \begin{cases}
    m & \text{if on antimicrobial therapy} \\ % & is your "\tab"-like command (it's a tab alignment character)
    1 & \text{otherwise.}
\end{cases}
$$

-   $m$ is the increased (or decreased) relative risk of infection/colonisation due to antimicrobial therapy,

@@

| Name                                                       | Value    | Description                                                             | Reference                |
|------------------|------------------|-------------------|------------------|
| Baseline (pre-outbreak) antimicrobial prescription rate    | 0.319    | Proportion of patients administered antimicrobials during admission     | @versporten2018          |
| Admission duration                                         | 8.3 days | Mean of a Poisson distribution                                          | @thehealthfoundation2023 |
| Proportion of toilets that are shared between \>1 patients | 0.6      | The remaining proportion (0.4) of toilets were dedicated to one patient | N/A                      |

@@

```{r}
#| eval: true
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| warning: false
#| label: fig-posterior-densities
#| fig-cap: "Changes in parameters during outbreak and enhanced infection control periods. Density plots show the posterior distributions of key simulation parameters after calibration using approximate Bayesian computation."
#| fig-subcap:
#|   - "General parameters"
#|   - "Toilet-related parameters"
#| layout-ncol: 1
abc_params_outbreak_control$unadj.values %>% 
  as_tibble %>% 
  dplyr::select(-`outbreak-start`, -`outbreak-end`, -`control-end`,
                -`antibiotic-effect`,
                -`random-colonisation`) %>% 
  dplyr::select(!contains("toilet")) %>% 
  pivot_longer(cols=everything()) %>%
  mutate(type = case_when(
    str_starts(name, "o-") ~ "Outbreak",
    str_starts(name, "c-") ~ "Control",
    .default = "Baseline")) %>%
  mutate(name = str_remove(name, "^o-|^c-")) %>%
  mutate(name = str_replace_all(name, "-", " ")) %>%
  mutate(name = str_to_title(name)) %>% 
  # change type to ordered factor
  mutate(type = factor(type, levels = c("Baseline", "Outbreak", "Control"))) %>%
  ggplot(aes(x = value, ..scaled.., fill = type)) +
  geom_density(alpha = 0.1) +
  facet_wrap(~name, scales = "free_x") +
  # remove y axis
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("Parameter value") + 
  theme(legend.title = element_blank(),
        text=element_text(size=24)) + 
  # manually set colors
  scale_fill_manual(values = c("Baseline" = "green", "Outbreak" = "red", "Control" = "blue"))
